Spatiotemporal models of DO

### 2020-11-14 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
recheck for SST effect; plot covariate effects, residuals, and spatial random fields

```{r setup}
library(tidyverse)
library(sdmTMB)
# library(future)
library(dplyr)
```

@@

Current temperature model
```{r}
spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 800)
plot_spde(spde)
```

```{r eval = F}
m_temp_rw <- sdmTMB(
  temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl,
  ar1_fields = TRUE, # changed AR1 to true
  include_spatial = TRUE, 
  time = "year", spde = spde, 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)

saveRDS(m_temp_rw, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds")))
```

@@

Model diagnostics functions
```{r}
get_diag <- function(m, response = "log_do", variable = "depth_scaled") {
  predictions <- predict(m)
  predictions$residuals <- residuals(m)

  plot_map <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", colour = column)) +
      geom_point() +
      coord_fixed()
  }

  g <- ggplot(predictions, aes_string("est", response)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~year) +
    coord_fixed() +
    geom_abline()
  print(g)

  g <- ggplot(predictions, aes(est, residuals)) +
    geom_point(alpha = 0.2) +
    geom_smooth()
  print(g)

  g <- ggplot(predictions, aes_string(variable, "residuals")) +
    geom_point(alpha = 0.2) +
    geom_smooth() +
    facet_wrap(~year)
  print(g)

  g <- ggplot(predictions, aes(X, Y, colour = residuals)) +
    geom_point(alpha = 0.2) +
    coord_fixed() +
    scale_color_gradient2()+
    facet_wrap(~year)
  print(g)

@@

Load and prep SST data
```{r eval=FALSE}
all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-meanSST-all.rds"))
# all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-processed.rds")) # no SST
# glimpse(all_sensor)

@@

d_trawl2[is.na(d_trawl2$shallow), ]
d_trawl2[is.na(d_trawl2$SST_scaled), ]

# glimpse(d_trawl2)
```

@@

Does a fixed interaction with SST_scaled do any better?
```{r}
spde2 <- make_spde(d_trawl2$X, d_trawl2$Y, n_knots = 500)
plot_spde(spde2)
```

```{r eval=FALSE}
m_temp2 <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + DOY_scaled * shallow + DOY_scaled2 * shallow,
  data = d_trawl2,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde2, family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp2, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY.rds")))

m_temp2
```

```{r eval=FALSE}
m_temp3 <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow + DOY_scaled * shallow + DOY_scaled2 * shallow,
  data = d_trawl2,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde2, family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp3, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST.rds")))

m_temp3
```

@@

```{r eval=FALSE}
get_diag(m_temp3, response = "temperature_c", variable = "depth_scaled")
```

@@

saveRDS(p_nd, file = "../VOCC/data/predicted_temp_allyears_800kn.rds")
```

```{r}
# p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank())
}

@@

@@

```{r}
omega_s_all <- plot_map_raster(p_nd, "omega_s") +
  ggtitle("Spatial random effects only") +
    scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +  labs(fill = "") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = c(.82,.75))

omega_s_all
```

@@

(st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_wrap(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
  labs(fill = "epsilon") + 
  gfplot::theme_pbs() + 
  theme(
  legend.position = "none", 
  axis.title.x = element_blank(), axis.title.y = element_blank()))

@@

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) #%>% filter(ssid!=4)
st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
     scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
          labs(fill = " ") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = c(.85,.15))
st_4
```

```{r}
p_nd16 <- p_nd %>% filter(ssid==16) #%>% filter(ssid!=4)
st_16 <- plot_map_raster(p_nd16, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +
  xlim(65,345) +
    ylim(5800,6100) +
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
st_16
```

>>>>

```{r setup}
library(tidyverse)
library(sdmTMB)
# library(future)
library(dplyr)
library(gfranges)

plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(
  axis.title = element_blank(), 
  axis.ticks = element_blank(),
  axis.text = element_blank()
  )
}
```

Model diagnostics function
```{r}
get_diag <- function(m, response = "temperature_c", variable = "depth_scaled", colour_var = "depth", start_year = 2007, ssids = c(1,3,4,16)) {
  predictions <- predict(m)
  predictions$residuals <- residuals(m)

  predictions <- predictions %>% filter (year >= start_year)

  plot_map <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", colour = column)) +
      geom_point() +
      coord_fixed()+
      gfplot::theme_pbs() 
  }

  g <- ggplot(predictions, aes_string("est", response)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~year) +
    coord_fixed() +
    geom_abline()+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(est, residuals)) +
    geom_point(alpha = 0.2) +
    geom_smooth()+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 1.2) +
    geom_smooth(colour="grey", size = 1.2) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    # facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(
      axis.text.y = element_text(size = 14),
      axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)

  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 0.7) +
    geom_smooth(colour="grey", size = 0.7) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)

    g <- ggplot(filter(predictions, ssid %in% ssids), aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 1) +
    geom_smooth(colour="grey", size = 1) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    facet_wrap(~ssid, scales = "free_x")+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(X, Y, colour = residuals)) +
    geom_point(alpha = 0.2) +
    coord_fixed() +
    scale_color_gradient2() +
    facet_wrap(~year)+
    gfplot::theme_pbs() 
  print(g)

@@

Current temperature model
```{r}
spde <- sdmTMB::make_mesh(d_trawl, c("X", "Y"), n_knots = 800, type = "kmeans")
plot(spde)
```
Original model code
```{r eval = F}
# spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 800)
# m_temp_rw <- sdmTMB(
#   temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
#   time_varying = ~ 0 + depth_scaled + depth_scaled2,
#   data = d_trawl,
#   ar1_fields = TRUE, # changed AR1 to true
#   include_spatial = TRUE, 
#   time = "year", spde = spde, 
#   family = gaussian(link = "identity"),
#   nlminb_loops = 2,
#   newton_steps = 1,
#   silent = FALSE
# )
# saveRDS(m_temp_rw, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds")))
```

New CV model code
```{r eval = F}
m_temp_cv <- sdmTMB_cv(
  temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl,
  ar1_fields = TRUE, # changed AR1 to true
  include_spatial = TRUE, 
  time = "year", spde = spde, 
  family = gaussian(link = "identity"),
  k_folds = 5,
  # nlminb_loops = 2,
  # newton_steps = 1,
  silent = FALSE
)
saveRDS(m_temp_cv, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-cv.rds")))

m_temp_cv <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-cv.rds")))
m_temp_cv$fold_loglik
m_temp_cv$sum_loglik
m_temp_cv$max_gradients
```

@@

@@

Load and prep SST data
```{r eval=FALSE}
# all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-meanSST-all.rds"))
# # all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-processed.rds")) # no SST
# # glimpse(all_sensor)
# 
# all_depth <- all_sensor %>%
#   # filter(depth_max>10) %>% # maybe we should filter incase missing depth values also indicate a sensor fail?
#   # filter missing location data and trial year
#   dplyr::filter(!is.na(latitude), !is.na(longitude)) %>%
# 
#   # convert lat and lon to UTMs
#   dplyr::mutate(X = longitude, Y = latitude) %>%
#   gfplot:::ll2utm(., utm_zone = 9) %>% 
# 
#   # interpolate missing depth values
#   dplyr::rename(depth = depth_m) %>%
#   gfplot:::interp_survey_bathymetry()

# d_trawl <- all_depth$data %>% 
#   # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
#   filter(depth_max>10) %>% 
#   gfplot:::scale_survey_predictors()

olddata <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-400kn.rds"))) 
d_trawl <- olddata$data

@@

# d_trawl2[is.na(d_trawl2$shallow), ]
# d_trawl2[is.na(d_trawl2$SST_scaled), ]
```

@@

Does a fixed interaction with SST_scaled do any better?
Rerun main model with SST dataset for comparisons
```{r}
spde <- make_mesh(d_trawl2, c("X", "Y"), n_knots = 800)

m_temp_new <- sdmTMB(
  temperature_c ~ 0 + as.factor(year), 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl2, spde = spde,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)
saveRDS(m_temp_new, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-sstdata.rds")))
m_temp_new
AIC(m_temp_new)
```

```{r}
spde <- make_mesh(d_trawl2, c("X", "Y"), n_knots = 800)

m_temp_sst <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow, 
  data = d_trawl2, spde = spde,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp_sst, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-SST.rds")))
m_temp_sst
AIC(m_temp_sst)
```

```{r}
m_temp_new <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-sstdata.rds")))
m_temp_sst <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-SST.rds")))
get_diag(m_temp_new, response = "temperature_c")
get_diag(m_temp_sst, response = "temperature_c")
```

# try with fewer knots
```{r eval = F}
spde3 <- sdmTMB::make_mesh(d_trawl2, c("X", "Y"), n_knots = 400, type = "kmeans")

m_temp1aic <- sdmTMB(
  temperature_c ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl2, spde = spde3,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)
saveRDS(m_temp1aic, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-400kn-new.rds")))

m_temp1aic <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-400kn-new.rds")))
# m_temp1aic<- sdmTMB:::update_model(m_temp1aic)
AIC(m_temp1aic)
```

Run CV on main model
```{r}
# spde2 <- make_spde(d_trawl2$X, d_trawl2$Y, n_knots = 800)
spde2 <- sdmTMB::make_mesh(d_trawl2, c("X", "Y"), n_knots = 200, type = "kmeans")
plot(spde2)
```

```{r}
m_temp1 <- sdmTMB_cv(
  temperature_c ~ 0 + as.factor(year), 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl2, spde = spde3, 
  ar1_fields = TRUE, 
  include_spatial = TRUE, 
  time = "year", 
  family = gaussian(link = "identity"),
  k_folds = 20,
  # nlminb_loops = 2,
  # newton_steps = 1,
  silent = FALSE
)
# saveRDS(m_temp1, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-400kn-cv20.rds")))
saveRDS(m_temp1, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-150kn-cv20.rds")))

# m_temp1 <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-300kn-cv.rds")))
m_temp1$fold_loglik
m_temp1$sum_loglik
m_temp1$max_gradients
m_temp1$pdHess
```

Check if DOY helps model
```{r eval=FALSE}
spde3 <- sdmTMB::make_mesh(d_trawl2, c("X", "Y"), n_knots = 400, type = "kmeans")

m_temp2aic <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + DOY_scaled + DOY_scaled2,
  data = d_trawl2, spde = spde3, 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  # k_folds = 20,
  silent = TRUE
)

saveRDS(m_temp2aic, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY-400kn.rds")))
m_temp2aic <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY-400kn.rds")))
m_temp2aic
AIC(m_temp2aic)

# m_temp2cv <- sdmTMB_cv(
#   temperature_c ~ 0 + as.factor(year) + DOY_scaled + DOY_scaled2,
#   data = d_trawl2, spde = spde2, 
#   time_varying = ~ 0 + depth_scaled + depth_scaled2,
#   ar1_fields = TRUE, 
#   include_spatial = TRUE,
#   time = "year", 
#   family = gaussian(link = "identity"),
#   # nlminb_loops = 2,
#   # newton_steps = 1,
#   k_folds = 20,
#   silent = TRUE
# )
# 
# saveRDS(m_temp2, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY-cv20.rds")))
# m_temp2cv <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-DOY-cv20.rds")))
# m_temp2cv
# m_temp2cv$fold_loglik
# m_temp2cv$sum_loglik
# m_temp2cv$max_gradients
```

Check if SST helps model 
```{r}
m_temp3aic <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow, 
  data = d_trawl2, spde = spde3, 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)
saveRDS(m_temp3aic, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-400kn.rds")))
# m_temp3aic <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-400kn.rds"))
m_temp3aic <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-400kn.rds")))
AIC(m_temp1aic, m_temp2aic, m_temp3aic)

m_temp3aic
```

Check if SST and DOY help model
```{r eval=FALSE}
m_temp4aic <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * DOY_scaled * shallow, 
  data = d_trawl2, spde = spde3, 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)
saveRDS(m_temp4aic, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-DOY-400kn.rds")))

m_temp4aic <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-DOY-400kn.rds"))
# m_temp4aic
AIC(m_temp1aic, m_temp2aic,  m_temp3aic, m_temp4aic)
```

```{r eval=FALSE}
m_temp3 <- sdmTMB_cv(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow, 
  data = d_trawl2, spde = spde2, 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  # nlminb_loops = 2,
  # newton_steps = 1,
  k_folds = 20,
  silent = TRUE
)

# 500 knot early version
# saveRDS(m_temp3, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST.rds")))

# new 800 knot version for cross validation
saveRDS(m_temp3, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-cv20.rds")))

# m_temp3 <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-cv20.rds"))
# m_temp3
m_temp3$fold_loglik
m_temp3$sum_loglik
m_temp3$max_gradients
```

Check if SST and DOY help model using cv
```{r eval=FALSE}
m_temp4 <- sdmTMB_cv(
  temperature_c ~ 0 + as.factor(year) + SST_scaled * shallow + SST_scaled * DOY_scaled * shallow, 
  data = d_trawl2, spde = spde2, 
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  # nlminb_loops = 2,
  # newton_steps = 1,
  k_folds = 20,
  silent = TRUE
)

# 500 knot early version
# saveRDS(m_temp3, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST.rds")))

# new 800 knot version for cross validation
saveRDS(m_temp4, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-DOY-cv20.rds")))

# m_temp4 <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST-DOY-cv20.rds"))
# m_temp4
m_temp4$fold_loglik
m_temp4$sum_loglik
m_temp4$max_gradients
m_temp4$pdHess
```

```{r}
m_temp_sst <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-SST.rds"))

m_temp_sst <- sdmTMB:::update_model(m_temp_sst)

@@

```{r eval=FALSE}
get_diag(m_temp_new, response = "temperature_c", variable = "depth_scaled", colour_var = "depth", start_year = 2002)
get_diag(m_temp_new, response = "temperature_c", variable = "DOY", colour_var = "depth", start_year = 2002, ssids = c(1,3,4, 16))
```

@@

# saveRDS(p_nd, file = "../VOCC/data/predicted_temp_allyears_800kn.rds")
```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

@@

Time-varying depth 
```{r eval}
# pd <- expand.grid(
#   depth_scaled = seq(min(m_temp_rw$data$depth_scaled),
#     max(m_temp_rw$data$depth_scaled), length.out = 50),
#   year = unique(m_temp_rw$data$year)
# )
# pd$depth_scaled2 <- pd$depth_scaled^2
# 
# # p <- predict(m_temp_rw, newdata = pd, se_fit = TRUE, re_form = NA, xy_cols = c("X", "Y"))
# p <- predict(m_temp_new, newdata = pd, se_fit = TRUE, re_form = NA)
# 
# p$Depth <- exp(p$depth_scaled*0.661 + 5.07)
# p$Temperature <- p$est
# # 
# p$lowCI <- (p$est - 1.96 * p$est_se)
# p$highCI <- (p$est + 1.96 * p$est_se)
# # 
# saveRDS(p, here::here("analysis/tmb-sensor-explore/data/depth-tv-m-temp-rw-800-kn.rds"))
p <- readRDS(here::here("analysis/tmb-sensor-explore/data/depth-tv-m-temp-rw-800-kn.rds"))

ggplot(filter(p, Depth >15 & year >2007), aes(Depth, Temperature,
  ymin = lowCI, 
  ymax = highCI, 
  group = as.factor(year), fill=year, colour = year)) +
  geom_line(size = 0.5, alpha =0.85) +
  # geom_smooth(method= "loess", size = 0.4, alpha =0.85, se =F ) +
  # geom_smooth(span = 0.5, size = 0.4, alpha =0.85, se =F ) +
  scale_fill_viridis_c(option = "C") +
  scale_colour_viridis_c(option = "C") +
  # ylab("DO") +
  geom_ribbon(alpha = 0.2, colour = NA) +
  # scale_y_continuous(limits = c(0,4.5)) +
  scale_x_reverse(limits = c(600,20)) +
  ylim( 2, 15) +
  coord_flip() +
  # scale_x_continuous(limits = c(18,210)) +
  gfplot::theme_pbs() +
  theme(legend.position = c(.8,.4))
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/depth-tv-m-temp-rw-800-kn.png"), width = 3, height = 2.5)

# ggplot(filter(p, Depth >15 & year == 2018), aes(Depth, Temperature,
#   ymin = (Temperature - 1.96 * est_se), 
#   ymax = (Temperature + 1.96 * est_se))) +
#   geom_line(size = 1.5, alpha =0.85) + 
#   # scale_color_viridis_c(option = "C") +
#   geom_ribbon(alpha=0.2) +
#   scale_x_reverse(limits = c(210,20)) +
#   ylim(5, 15) +
#   coord_flip() +
#   gfplot::theme_pbs() + 
#   theme(legend.position = c(.8,.4))

@@

```{r}
(omega_s_all <- plot_map_raster(p_nd, "omega_s") +
  ggtitle("Spatial random effects only") +
    scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +  labs(fill = "") + theme(legend.position = c(0.2, 0.3))
  )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/omegas-temp-rw-800-kn.png"), width = 3, height = 3)

omega_s_all

@@

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd1 <- p_nd %>% filter(ssid!=16) %>% filter(ssid!=4) %>% filter(year>2007)

(st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_grid(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
  labs(fill = "epsilon") + 
  theme(
  legend.position = "none"))

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-1n3.png"), width =6, height = 2)

@@

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd4 <- p_nd %>% filter(ssid==4) %>% filter(year>2007)#%>% filter(ssid!=4)
(st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_grid(~year) +
     scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
          labs(fill = " ") + theme( legend.position = "none") )
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-4.png"), width = 6, height = 2)

st_4
```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd16 <- p_nd %>% filter(ssid==16) %>% filter(year>2007)#%>% filter(ssid!=4)
(st_16 <- plot_map_raster(p_nd16, "epsilon_st") +
  #ggtitle(" ") +
  facet_grid(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +
  xlim(20,360) + ylim(5850,6050)+ 
  # xlim(65,345) + ylim(5800,6100)+ 
    theme(panel.border = element_blank(), legend.position = "none") )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-16.png"), width = 6, height = 1)
st_16
```
